Predicting Manner of Exercise
======================================================
##Tiffani Heaberlin

##Overview 
In this assignment, predicting the manner of exercise for 20 subjects.

##Reading in Data
We have a dataset of 19,622 observations and 160 columns.  The first columns is
simply the row number.  The data will be read in.
```{r}
setwd("C:/Users/slussetc/Documents/GitHub/Machine_Learning")
library("caret")
set.seed(200)
training<-read.csv("TrainingData.csv")
```
##Model Training
I am a firm believer in less is more when it comes to the amount of predictors
in a model.  If the prediction is accurate with fewer predictors, it can make it
easier to explain and also means your chances of overfitting are reduced.  Due
to that, I decided to just use the initial set of 5 columns past the identifiers.
These were: new_window, num_window, roll_belt, pitch_belt, yaw_belt.
```{r}
traindata<-training[,c(6:10,160)]
traindata<-na.omit(traindata)
modelfit <- train(classe~.,data=traindata,method="knn")
modelfit
```
##Prediction of Test Data
Due to the accuracy of the inital model run, I used that to predict the classe
of the 20 test subjects.  The predictions were successful when submitted.  I
utilized the function supplied by the instructor to create the submission files.
```{r}
testing<-read.csv("TestData.csv")
testpred<-predict(modelfit,testing)
setwd("TestPredictions")
pml_write_files = function(x){
  n = length(x)
  for(i in 1:n){
    filename = paste0("problem_id_",i,".txt")
    write.table(x[i],file=filename,quote=FALSE,row.names=FALSE,col.names=FALSE)
  }
}
pml_write_files(testpred)
```
